% !TEX root = main.tex
\documentclass[a4paper, UKenglish, 11pt]{uiomaster}
\usepackage{lipsum}
\usepackage[subpreambles=true]{standalone}

\begin{document}

\chapter{Acknowledgements}
I want to express my gratitude to Gaute Einevoll for being a source of inspiration and guiding me toward the field of computational neuroscience. In addition to all your knowledge, I admire your always good humor and pleasant nature.

I would also like to extend massive thanks to Torbjørn Ness for his continues presence, patient guidance, enjoyable meetings, and for helping me navigate my work, which has contributed significantly to my learning and growth. Your willingness to answer my numerous questions has been invaluable during the work on this thesis.

A big thank you also goes to my fellow students in the office, who have enriched my time as a master's student with insightful conversations, support, and pleasant days.

Thanks to Andrea and Hedvig for being the best of friends throughout my studies. All the academic discussions, your unwavering support, the ups and downs we have faced together, and the fun we have had mean the world to me.

Moreover, my heartfelt appreciation goes to all my family and childhood friends for their continuous support, interest in my work, and kind words that have kept me motivated and focused.

Lastly, I want to offer my deepest appreciation to Vegard Falmår for being a constant presence in my life. Thank you for being genuinely interested in my work, thank you for being a machine learning expert and the fastest code debugger. Thank you for expecting a lot from me, challenging me academically, and helping me become a better version of myself. I am truly grateful for your presence throughout all my years at the university and for being the best discussion partner throughout my work on the thesis.


\end{document}
